% Beispiel eines Kapitels für die Latex-Vorlage am ETI.
%--------------------------------------------------------------------
%
%   Version: 3.25        (Koma-Skript, documentclass{scrbook})
%   Datum: 01.06.2018
%   Autor: Johannes Bier
%
%--------------------------------------------------------------------

\chapter{Task 2: Machine Behavior at \SI{15000}{\per\minute} and Maximum Power}

The maximum speed of a \gls{PMSM} is limited on one hand by mechanical constraints, such as the mechanical strength of the rotor (circumferential speed), the bearings, allowable imbalances, etc.

On the other hand, the speed cannot be increased indefinitely from an electrical perspective. Once the torque-speed curve, which decreases with increasing speed, intersects the horizontal axis, the theoretical speed limit is reached. This point depends on the electromagnetic design of the machine. For the motor under consideration here, the maximum speed is mechanically limited to \SI{15000}{\per\minute}. 

In Task 2, the electromagnetic properties at this limit shall be examined.

\bigskip

Tasks:
\begin{enumerate}
	\item Present the torque and torque ripple at \SI{15000}{\per\minute}.
	\item Visualize the magnetic flux density distribution of the motor at \SI{0}{\second}.
	\item Calculate the hysteresis losses, eddy current losses, and additional losses.
	\item Calculate the magnet losses.
	\item Calculate the efficiency at this operating point.
\end{enumerate}

Please note the following:
\begin{itemize}
	\item At \SI{15000}{\per\minute}, the stator resistance is still assumed to be \SI{0.0228}{\ohm}.\\ 
	The influence of skin/proximity effects on the stator resistance is not accounted for.
	\item Only the average loss values in steady-state operation should be considered.
	\item Bearing losses at \SI{15000}{\per\minute} are assumed to be \SI{13.2}{\watt}.
	\item For efficiency calculation, you may use \autoref{eq:Wirkungsgradberechnung}. Other losses can be neglected.
\end{itemize}

\newpage

\section{Average torque and torque ripple at \SI{15000}{\per\minute}}

\section{Magnetic flux density distribution of the motor at \SI{0}{\second}}

\section{Hysteresis, eddy current, and additional losses}

\section{Magnet losses}

\section{Efficiency at maximum speed, maximum power}

\newpage